---
title: "axBoost Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{axBoost Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(axBoost)
```

<!-- Install vignette with devtools::install(build_vignettes = TRUE) on the console -->

The package axBoost contains a collection of rather unrelated functions, which 
I found useful to have them exported and available as an own package. At the
moment of writing, the functions mainly help to visualize correlations between 
many variables in a large data set (~ 300 variables). For example, this includes 
functions to plot a correlogram or to plot double dissocitations
(e.g., Asendorpf, Banse, and Mücke, 2002) with and without moderator effects.
The functions generating a plot are described below in this vignette, the 
functionality of functions without graphical output is explained in the example 
part of the help page of the function.


Asendorpf, J. B., Banse, R., & Mücke, D. (2002). Double dissociation
between implicit and explicit personality self-concept: The case of shy
behavior. *Journal of Personality and Social Psychology, 83*(2), 380–393.

# The function axCorrgram()

A correlogram of a matrix / data frame is plotted. In the upper right triangle 
the size of correlations are depicted. Red and blue indicate that the 
correlations are significant, either positive (red) or negative (blue), also 
marked with a "*". Marginal significant correlations are colored with darkred 
(positive) and darkblue (negative), additionally marked with a "+". This is
helpful to detect patterns and structures in the data.
The diagnoal contains the variable names with a histogram. The lower left 
triangle depicts a scatter plot with a lowess line. This helps for searching for
potential outliers. Up to 16 variables can be correlated  in one correlogram.
The option fontsize is used to adapt the size of the correlations in the upper
right to the size of the boxes.

```{r, fig.dim = c(8, 6), out.width = "100%"}
axCorrgram(axBoost::df1, fontsize = .7)
```

# The function modRegGraph()

This Function plots a moderated regression interaction diagramm and returns the 
coordinates of the points pred_H_mod_H pred_H_mod_L pred_L_mod_H pred_L_mod_L 
to be used elswhere (e.g., in another plot). H denotes high (+1 SD), L denotes 
low (-1 SD).


```{r}
reg1 <- lm(AutoBehav ~ IndMeasure * mod, data = df1)
summary(reg1)
```

```{r, fig.dim = c(6, 6), out.width = "60%"}
modRegGraph(coef(reg1), pred = "IndMeasure", mod = "mod", crit = "AutoBehav", plotRange = 1.7)
```


# The function drawDD()

This function draws a double dissociation. This means that two regressions have 
to be computed. Because this is very prone to error when done by hand, the best 
way to use this function is in a loop, with predefined predictors, criteria and
moderators. The figure below shows a double dissociation with a moderator.

The function is quite versatile and allows to

* include moderators (optionally on both paths of a regression)
* include covariates
* compute robust regressions (using the robust and WRS2 packages)
* use the residuals of the covariates as criteria
* optionally print the output of the lm() and cor() functions

```{r, fig.dim = c(8, 6), out.width = "100%"}
drawDD(data = axBoost::df1, predUpper = "IndMeasure", predLower = "DirMeasure", 
  critUpper = "AutoBehav", critLower = "ContrBehav", moderator = "mod", 
  title = "Testplot", printReg = TRUE)
```

